### 2017-07-21 sheets/talk-12/sheet-12.tex
Fix some exercises for talk 12

    \item
      $\rho \of (1 \otimes f) \of \alpha \of (\sigma \otimes 1)
        = \lambda \of (f \otimes 1) \of \alpha^{-1} \of (1 \otimes \sigma) \of \alpha$ \\
      for $A \otimes B \xrightarrow{f} f$.
  \end{enumerate}
\end{exercise}

@@

\pagebreak
\begin{exercise}
  Verify the correctness of the following graphical equations by
  \begin{enumerate}
    \item the correctness theorem of the graphical calculus,
    \item substitution in string diagrams using the axioms of braided monoidal categories,
    \item construction of a commuting diagram from the axioms.
  \end{enumerate}
  \begin{enumerate}[label=(\roman*)]
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_1}}}$
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_2}}}$
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_3}}}$
      ($\sigma_{A, I} = \lambda_{A}^{-1} \of \rho_A$)
  \end{enumerate}
\end{exercise}

@@

\begin{exercise}
  Show that in a monoidal category where all idempotents split, if there are morphisms $I \xrightarrow{\eta} R \otimes L$ and $L \otimes R \xrightarrow{\varepsilon} I$ satisfying one of the snake equations, then $L$ has a right dual (not necessarily $R$).
\end{exercise}

>>>>

    \item
      $\rho \of (1 \otimes f) \of \alpha \of (\sigma \otimes 1)
        = \lambda \of (f \otimes 1) \of \alpha^{-1} \of (1 \otimes \sigma) \of \alpha$ \\
      for $A \otimes B \xrightarrow{f} I$.
  \end{enumerate}
\end{exercise}

@@

\pagebreak
\begin{exercise}
  Verify the correctness of the following graphical equations in braided monoidal categories by
  \begin{enumerate}
    \item the correctness theorem of the graphical calculus,
    \item substitution in string diagrams using the axioms of braided monoidal categories and the correctness theorem for the graphical calculus on general monoidal categories,
    \item construction of a commuting diagram from the axioms and the coherence theorem for general monoidal categories.
  \end{enumerate}
  \begin{enumerate}[label=(\roman*)]
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_1}}}$
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_2}}}$
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_3}}}$
      ($\sigma_{A, I} = \lambda_{A}^{-1} \of \rho_A$)
  \end{enumerate}
\end{exercise}

@@

\begin{exercise}
  Show that in a monoidal category where all idempotents split, if there are morphisms $I \xrightarrow{\eta} R \otimes L$ and $L \otimes R \xrightarrow{\varepsilon} I$ satisfying one of the snake equations, then $L$ has a right dual (not necessarily given by $R$ with $\eta$ and $\varepsilon$).
\end{exercise}
